Projecting genetic associations through gene expression patterns highlights disease etiology and drug mechanisms

### 2023-06-13 output/latex/manuscript.tex
latex: add authors' affiliations section
add "code and data availability" as top section

@@

\hypertarget{code-and-data-availability}{%
\subsubsection{Code and data availability}\label{code-and-data-availability}}

The code and data to reproduce all the analyses in this work are available in \url{https://github.com/greenelab/phenoplier}.

>>>>

\hypertarget{affiliations}{%
\subsection{Affiliations}\label{affiliations}}

@@

\hypertarget{code-and-data-availability}{%
\subsection{Code and data availability}\label{code-and-data-availability}}

The code and data to reproduce all the analyses in this work are available at \url{https://github.com/greenelab/phenoplier}.
